Twists of supersymmetric gauge theories

### 2019-09-06 paper.tex

The most general theory $4$-dimensional $\mc N = 1$ theory we will consider is super Yang-Mills theory valued in a Lie algebra $\fg$ coupled to a chiral multiplet with values in a complex $\fg$-representation $R$. 
This means that the fields $\phi, \psi_+$ take values in $R$ and $\Bar{\phi}, \psi_-$ take values in $R^*$. 
We have written down the action for supersymmetric Yang-Mills theory numerous times. 
The kinetic part of the action functional for $4$-dimensional $\mc N = 1$ matter is of the form
\[
S_{\rm matter} (\phi, \Bar{\phi}, \psi_+, \psi_-) = \int \d^4 x \; \<\partial_{x_i} \phi , \partial_{x_i} \Bar{\phi}\>_R + \int \d^4 x \; \<\psi_+ , \sd \dd \psi_-\>_R .
\]
Here $\<-,-\>_R$ incorporates the obvious pairing between $R$ and $R^*$. 
Super Yang-Mills couples to the matter via the action 
\[
S_{\rm couple} = \int \d^4 x \;
\]

The action of supersymmetry on the $4$-dimensional matter theory is encoded by a linear and quadratic functional:
\begin{align*}
I^{(1)} (Q_+, Q_-) & = \int \<\phi^*, (Q_+, \psi_+)\>_R + \int \<\Bar{\phi}^*, (Q_-, \psi_-)\>_R + \int \<\psi^*_+, \rho(\d \phi) Q_+ \>_R + \int \<\psi_-^*, \rho(\d \Bar{\phi}) Q_-\>_R \\
I^{(2)} (Q_+ \otimes Q_-) & = \int \<\psi^*_- , \rho(\Gamma(Q_+, Q_-)) \psi_+\>_R.
\end{align*}

>>>>

The most general theory $4$-dimensional $\mc N = 1$ theory we will consider is super Yang-Mills theory valued in a Lie algebra $\fg$ coupled to a chiral multiplet with values in a complex $\fg$-representation $R$. 
This means that the fields $\phi, \psi_+$ take values in $R$ and $\Bar{\phi}, \psi_-$ take values in $R^*$. 
We have written down the action for supersymmetric Yang-Mills theory numerous times. 
The kinetic part of the action functional for $4$-dimensional $\mc N = 1$ matter is of the form
\[
S_{\rm matter} (\phi, \Bar{\phi}, \psi_+, \psi_-) = \int \d^4 x \; \<\partial_{x_i} \phi , \partial_{x_i} \Bar{\phi}\>_R + \int \d^4 x \; \<\psi_+ , \sd \dd \psi_-\>_R .
\]

Here $\<-,-\>_R$ incorporates the obvious pairing between $R$ and $R^*$. 
Super Yang-Mills couples to the matter via the action 
\[
S_{\rm couple} = \int \d^4 x \;
\]
Let $S_{\rm BV}$ denote the full BV action of $\mc N = 1$ super Yang-Mills coupled to matter.

The BV action is clearly Poincar\'{e} invariant, so there is an interaction $I_{\rm Poin}$ encoding the action by the $4$-dimensional Poincar\'{e} algebra.

The action of supersymmetry on the $4$-dimensional matter theory is encoded by a linear and quadratic functional:
\begin{align*}
I^{(1)} (Q_+, Q_-) & = \int \<\phi^*, (Q_+, \psi_+)\>_R + \int \<\Bar{\phi}^*, (Q_-, \psi_-)\>_R + \int \<\psi^*_+, \rho(\d \phi) Q_+ \>_R + \int \<\psi_-^*, \rho(\d \Bar{\phi}) Q_-\>_R \\
I^{(2)} (Q_+ \otimes Q_-) & = \int \<\psi^*_- , \rho(\Gamma(Q_+, Q_-)) \psi_+\>_R.
\end{align*}
where $Q_\pm \in S_{\pm}$.

Also define $I^{(1)}_{\rm gauge}$ and $I^{(2)}_{\rm gauge}$. \brian{this is so similar to the 10d case. How do you suggest we do this?}

\begin{prop} 
Let $I^{(1)} = I^{(1)}_{\rm matter} + I^{(1)}_{\rm gauge}$ and $I^{(2)} = I^{(2)}_{\rm matter} + I^{(2)}_{\rm gauge}$. 
Then, the functional
\[
\fS = S_{\rm BV} + I_{\rm Poin} + I^{(1)} + I^{(2)} \in \clie^\bu(\mf A) \otimes \cloc^\bu(\fL) [-1]
\]
satisfies the Maurer-Cartan equation
\[
\left(\d_{\rm Lie} \fS + \frac{1}{2} \{\fS, \fS\} \right) = 0 .
\]
\end{prop}

Note that $I^{(1)}$ is linear in the supersymmetry algebra, and $I^{(2)}$ is quadratic.
Thus, the induced action on the $4$-dimensional $\mc N=1$ theory by the supersymmetry algebra $\mf A$ is an $L_\infty$ action.
